News Across Languages - Cross-Lingual Document Similarity and Event Tracking

### 2015-03-24 rupnik2015.tex

The term event is vague and ambiguous, but for the practical purposes we define it as ``any significant happening that is being reported about in the media''. Examples of events would include shooting down of the Malaysia Airlines plane over Ukraine on July 18th, 2014 and HSBC's admittance of aiding their clients in tax evasion on February 9th, 2015 (Figure \ref{}). Events such as these are covered by many articles and the question is how to find all the articles in different languages that are describing a single event.

@@

The paper is organized as follows: we first provide an overview of the system as a whole (Section ), followed by details on each of the two steps described above. We first introduce several approaches to measures of cross-lingual similarity (Section ) and then the algorithms for matching clusters to events.  To improve readability, we describe relevant related work for each module in its corresponding Section.
Finally, we present and interpret the experimental results and finally give conclusions and describe promising future directions.

\section{Pipeline}

@@

Our approach is based on first defining a similarity function between articles in different languages (Section~\ref{}) and then we present several efficient approaches to linking the clusters based on features (Section~\ref{}). First, however we describe the pre-processing on the input articles which we then take as input.

The system is designed to handle streams and so we describe how a document which enters the stream is processed.   A new document is first tokenized, stop words are removed and words are stemmed.
 What remains is represented in a vector-space model and normalized using $TF-IDF$ (see Section~\ref{} for the definition). Since each article is tagged with its language, cosine similiarity  is used to find the modst similar existing cluster, by comparing it to the centroid vector of each cluster. A selected threshold is used to determine if the article is not similar to any existing clusters (0.4 was used in our experiments).  The article is then assigned to the corresponding cluster, otherwise a new cluster is created, initially containing only the single article.

@@

 Further details about the system can be found in \cite{}, while our full pipeline is shown in Figure~\ref{}.

@@

\section{Cross-lingual Document Similarity}

Document similarity is an important component in techniques from text mining and natural language processing. Many techniques use the similarity as a black box, i.e., a kernel in Support Vector Machines. Comparison of documents (or other types of text snippets) is a well studied problem \todo{some references to prove that}. In this section we define document similarity in a cross-lingual setting, where the similarity function receives documents in different languages. We conclude the section by an introduction of \todo{two datasets} which we used in this paper to learn cross-lingual similarity functions.

@@

\textbf{Document representation.}

@@

\subsection{Canonical Correlation Analysis}
 The final approach is a statistical technique to analyze data from two sources - after which we will describe our main contribution to computing cross-lingual similarities.

@@

The main application on which we test the above similiarity is cross-lingual event linking. In online media streams -- particularly new articles -- there is often duplication of reporting, different viewpoints or opinions, all centering around a single event. Same events are covered by many articles and the question we address is how to find all the articles in different languages that are describing a single event. We base our evaluation on an online system for detection of world events, called Event Registry. We do not address the problem of detection of events in this paper but rather consider the problem that given a series of events, how may we best ``tag" or match articles in different languages to these events. The events are represented by clusters of articles and so ultimately our problem reduces to find suitable matchings between clusters with articles in different languages.

@@

Furthermore, the matching of clusters is a \emph{generalized matching}. We cannot assume that there is only one cluster per language per event, nor can we assume complete coverage - that there exists at least one cluster per event in every language. This implies that we cannot make any assumptions on the matching, e.g. one-to-one, complete, etc. This excludes the use of standard weighted bipartite matching type of algortihms for this problem.

@@

The problem in the second phase of the pipeline is to identify the clusters (given?) describing the same events. Each article $a_i$ is written in a language $l$, where $l \in L = \{l_1,l_2,...,l_k\}$. For each language $l$, we generate and maintain a set of language-specific clusters $C_l$. That is, all articles are in language $l$. For any cluster $c_i \in C_{l_a}$, we would like to identify clusters $c_j \in C_{l_b}$ (where $l_a \neq l_b$) that describe the same event as $c_i$. We define \emph{equivalent clusters} as  pairs $(c_i,c_j)$ such that both clusters in the pair describe the same event in languages $C_{l_a}$ and $C_{l_b}$ respectively.

@@

In order to identify clusters $c_j$ that are equivalent to cluster $c_i$, we have developed a two-stage algoirhtm. First, for a cluster $c_i$, we efficiently identify a small set of candidate clusters and then  find the clusters from among the candidates which are equivalent to $c_i$.

The details of the first step are described in Algorithm~\ref{cluster_merge_algo1}. The algorithm begins by individually inspecting each article $a_i$ in the cluster $c_i$. Using CCA  (see Section~\ref{}),  it then identifies the 10 most similar articles to $a_i$ in each language $l \in L$. For each  similar article $a_j$, we identify its corresponding  cluster $c_j$ and add it to the set of candidates. \todo{we should say a few words why this is more efficient - since now we are comparing each article to all other articles - while we said it is not feadible for clusters}. While the CCA simliarity is approximate, our  assumption  is that articles in different languages describing the same event, will generally have a higher similarity than articles about different events. While this assumption does not always hold, redundancy in the data mitigates these false positives. Since we compute the 10 most similar articles for each article in $c_i$, we are likely to identify all the relevant candidates for cluster $c_i$.

>>>>

The term event is vague and ambiguous, but for the practical purposes we define it as ``any significant happening that is being reported about in the media''. Examples of events would include shooting down of the Malaysia Airlines plane over Ukraine on July 18th, 2014 and HSBC's admittance of aiding their clients in tax evasion on February 9th, 2015 (Figure \ref{fig:event2}). Events such as these are covered by many articles and the question is how to find all the articles in different languages that are describing a single event.

\begin{figure}
\centering
\includegraphics[width=0.75\textwidth]{events2.png}
\caption{\label{fig:event2} Events are represented by collections of articles about an event, in this case the Malaysian airliner which was shot down over the Ukraine.}
\end{figure}

As input we consider a stream of articles in different languages and a list of events. Our goal is to assign articles to their corresponding events. A priori we do not know the coverage of the articles, that is not all the events may be covered and we do not know that all the articles necessarily fit into one of the events.  To achieve our goal, we divide the task into two parts: clustering the articles according to topic (regardless of language) and matching the clusters to events.

@@

The paper is organized as follows: we first provide an overview of the system as a whole (Section ~\ref{sec:pipeline}), followed by details on each of the two steps described above. We first introduce several approaches to measures of cross-lingual similarity (Section~\ref{sec:crosslingual}) and then the algorithms for matching clusters iin different languages(Section~\ref{sec:linking}).  To improve readability, we describe relevant related work for each module in its corresponding Section.
Finally, we present and interpret the experimental results and finally give conclusions and describe promising future directions.

\section{Pipeline}\label{sec:pipeline}

\begin{figure}[tb]
\centering
\includegraphics[width=0.75\textwidth]{pipeline1}
\caption{\label{fig:pipeline} Our pipeline - from the Event Registry we obtain a stream of multi-lingual documents and monolingual clusters. Our contribution is shown on the right, where using cross-lingual similarity, we link the clusters across languages which correspond to the same event.}
\end{figure}

@@

Our approach is based on first defining a similarity function between articles in different languages (Section~\ref{sec:crosslingual}) and then we present several efficient approaches to linking the clusters based on features (Section~\ref{sec:linking}). The pipeline is shown in Figure~\ref{fig:pipeline} First, however we describe the pre-processing on the input articles which we then take as input.

The system is designed to handle streams and so we describe how a document which enters the stream is processed. The sequence of operations is shown in  Figure~\ref{fig:erpipeline}.  A new document is first tokenized, stop words are removed and words are stemmed.
 What remains is represented in a vector-space model and normalized using $TF-IDF$ (see Section~\ref{sec:tfidf} for the definition). Since each article is tagged with its language, cosine similiarity  is used to find the modst similar existing cluster, by comparing it to the centroid vector of each cluster. A selected threshold is used to determine if the article is not similar to any existing clusters (0.4 was used in our experiments).  The article is then assigned to the corresponding cluster, otherwise a new cluster is created, initially containing only the single article.

@@

 Further details about the system can be found in \cite{}.

\begin{figure}[tbp]
\centering
\includegraphics[width=\textwidth]{ev_pipeline}
\caption{\label{fig:erpipeline}  The Event Registry pipeline, after obtaining the raw stream of multi-lingual news articles, it first cleans and processes articles individually. It then aggregates and clusters the articles into similar events (within each language) and finally provides an interface allowing us to query for articles.}
\end{figure}

@@

\section{Cross-lingual Document Similarity}
\label{sec:crosslingual}
Document similarity is an important component in techniques from text mining and natural language processing. Many techniques use the similarity as a black box, i.e., a kernel in Support Vector Machines. Comparison of documents (or other types of text snippets) is a well studied problem \todo{some references to prove that}. In this section we define document similarity in a cross-lingual setting, where the similarity function receives documents in different languages. We conclude the section by an introduction of \todo{two datasets} which we used in this paper to learn cross-lingual similarity functions.

@@

\subsection{Problem definition}
\label{sec:tfidf}
\textbf{Document representation.}

@@

\subsection{Canonical Correlation Analysis}\label{sec:CCA}
 The final approach is a statistical technique to analyze data from two sources - after which we will describe our main contribution to computing cross-lingual similarities.

@@

The main application on which we test the above similiarity is cross-lingual event linking. In online media streams -- particularly new articles -- there is often duplication of reporting, different viewpoints or opinions, all centering around a single event. Same events are covered by many articles and the question we address is how to find all the articles in different languages that are describing a single event. We base our evaluation on an online system for detection of world events, Event Registry. We do not address the problem of detection of events in this paper but rather consider the problem that given a series of events, how may we best ``tag" or match articles in different languages to these events. The events are represented by clusters of articles and so ultimately our problem reduces to find suitable matchings between clusters with articles in different languages.

@@

\begin{figure}[tb]
\centering
\includegraphics[width=0.6\textwidth]{clusters}
\caption{\label{fig:clusters}  Given clusters of articles in different languages, the goal of  linking is to match clusters which have similar content across languages. The challenge in linking is to overcome the errors in the clustering and differing content as well as make the approach scalable. Therefore, we first identify candidate clusters. }
\end{figure}

Furthermore, the matching of clusters is a \emph{generalized matching}. We cannot assume that there is only one cluster per language per event, nor can we assume complete coverage - that there exists at least one cluster per event in every language. This implies that we cannot make any assumptions on the matching, e.g. one-to-one, complete, etc. This excludes the use of standard weighted bipartite matching type of algortihms for this problem. An example is shown in Figure~\ref{fig:clusters}, where a cluster may contain articles which are closely matched with many clusters in a different language.

@@

The problem in the second phase of the pipeline is to identify the clusters (given?) describing the same events. Each article $a_i$ is written in a language $l$, where $l \in L = \{l_1,l_2,...,l_k\}$. For each language $l$, we generate and maintain a set of language-specific clusters $C_l$. That is, all articles are in language $l$. For any cluster $c_i \in C_{l_a}$, we would like to identify clusters $c_j \in C_{l_b}$ (where $l_a \neq l_b$) that describe the same event as $c_i$. We define \emph{equivalent clusters} as  pairs $(c_i,c_j)$ such that both clusters in the pair describe the same event in languages $C_{l_a}$ and $C_{l_b}$ respectively. For example in Figure~\ref{fig:clusters}

@@

In order to identify clusters $c_j$ that are equivalent to cluster $c_i$, we have developed a two-stage algoirhtm. First, for a cluster $c_i$, we efficiently identify a small set of candidate clusters and then  find the clusters from among the candidates which are equivalent to $c_i$. An example is  shown in  Figure~\ref{fig:clusters}.

The details of the first step are described in Algorithm~\ref{cluster_merge_algo1}. The algorithm begins by individually inspecting each article $a_i$ in the cluster $c_i$. Using CCA  (see Section~\ref{sec:CCA}),  it then identifies the 10 most similar articles to $a_i$ in each language $l \in L$. For each  similar article $a_j$, we identify its corresponding  cluster $c_j$ and add it to the set of candidates. \todo{we should say a few words why this is more efficient - since now we are comparing each article to all other articles - while we said it is not feadible for clusters}. While the CCA simliarity is approximate, our  assumption  is that articles in different languages describing the same event, will generally have a higher similarity than articles about different events. While this assumption does not always hold, redundancy in the data mitigates these false positives. Since we compute the 10 most similar articles for each article in $c_i$, we are likely to identify all the relevant candidates for cluster $c_i$.
